Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2017-12-01 CVPR16/Source/experiments2.tex
Created presentation and poster for mid west vision conference.
Fit into the phdpropoal single column format.
Changing noration to match rest of the document.

\section{Experiments}
\label{sec:experiments}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Association Experiments}
%\vspace{-0.2cm}
\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinities (BM)~\cite{Brox_Malik_2010}.

\begin{figure*}[!!t]
\centering
%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{\small Association errors on different sets of input point tracks. Numbers on the x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  Point tracks & Ours & BBox & BM & RAS\\
  \midrule
  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{\small Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Errors & Associations & Errors\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
	\rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\    
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The ``Errors" columns show the
probabilistic errors in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

@@

\begin{table}
  \begin{tabular}{lrr}
    \toprule
    Method & t & dim \\
    \midrule
    Point cloud fitting
    & 6.87 & 4.02\\
    Initialization by~\cite{Song_Chandraker_2014}
    & 5.61 & 3.23\\
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{table}

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table \ref{tab:localizationExperiment}. The average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies against the initialization using \cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, such as when only the back of a car is visible, we rely on 3D size priors). The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusions, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion. We use $\lambda_{\text{track}} = 1$, $\lambda_{\text{detect}} = 1$, $\lambda_{\text{dyn}} = 10$, $\lambda_{\text{size}} = 7$. Please refer to the supplementary material for a detailed list of parameter settings.

>>>>

\begin{wraptable}[8]{r}{0.5\textwidth}\scriptsize\centering
\begin{tabular}{lrrrr}
  \toprule
  Point tracks & Ours & BBox & BM & RAS\\
  \midrule
  Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
  All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{wraptable}
%
\section{Experiments}
\label{sec:experiments}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Association Experiments}
%\vspace{-0.2cm}

\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinities (BM)~\cite{Brox_Malik_2010}.

\begin{figure*}[!!t]
\centering
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
%\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{Association errors on different sets of input point tracks. Numbers on the x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Errors & Associations & Errors\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
	\rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\    
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{Qualitative results of the association experiment. The ``Associations" columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The ``Errors" columns show the
probabilistic errors in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

\begin{wraptable}[11]{r}{0.5\textwidth}\scriptsize\centering
  \begin{tabular}{lrr}
    \toprule
    Method & t & dim \\
    \midrule
    Point cloud fitting
    & 6.87 & 4.02\\
    Initialization by~\cite{Song_Chandraker_2014}
    & 5.61 & 3.23\\
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05  & {\bf 1.59}\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & {\bf 3.24}  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
  \label{tab:localizationExperiment}
\end{wraptable}

@@

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table \ref{tab:localizationExperiment}. The average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies against the initialization using \cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, such as when only the back of a car is visible, we rely on 3D size priors). The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusions, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bbS_k$ that accounts for occlusion. We use $\lambda_{\text{track}} = 1$, $\lambda_{\text{detect}} = 1$, $\lambda_{\text{dyn}} = 10$, $\lambda_{\text{size}} = 7$. Please refer to the supplementary material for a detailed list of parameter settings.

### 2017-12-01 CVPR16/Source/occlusion.tex
Changing noration to match rest of the document.

\begin{wrapfigure}[15]{r}{0.5\textwidth}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{wrapfigure}

\vspace{-0.3cm}
\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque and regions more likely to be free space considered more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as
\begin{align}
  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
\end{align}
where $\cL(\cdot)$ is the logistic function given by
\begin{align}
  \cL(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
\end{align}
with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance. We set $k = 10\ln({49})$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object. Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.

\vspace{-0.3cm}
\paragraph{Image formation}
Given the above occupancy representation of the scene, a point on an object is observed in the camera when precisely two conditions are satisfied. First, the backprojected ray from the observed image pixel is transmitted through free space until it reaches the object. Second, the ray encounters an opaque enough object surface and is reflected. More formally, the probability of observation of a point $\bx_j$ on object $O_i$ is given by
\begin{align}
P^{ij}_{\textit{observation}} = P^{ij}_{\textit{reflection}}P^{j}_{\textit{transmission}}.
\label{eq:imgform}
\end{align}
The reflection probability ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions. The forms of these two functions are described next.

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$. Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$. Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$ as
\begin{align}
   \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
\label{eq:evalPrefl}
\end{align}
The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero. Here, $Z$ denotes the normalization factor. We note that in the extreme case of an object being fully opaque (that is, $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection. Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.

\vspace{-0.3cm}
\paragraph{Transmission probability}
\label{sec:ptransmission}
Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects. A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert law as
\begin{align}
I(\alpha) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function summed over all objects, $\occftot = \sum_i \occf$. Further, the domain of our occupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P^j_{\textit{transmission}}(\lambda + d\lambda) = P^j_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
Thus, for an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{c}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda}.
\label{eq:ptrans-integral}
\end{align}
Here, $\prod_{c}^{\lambda}$ represents a \emph{product integral} from $c$ to $\lambda$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain 
\vspace{-0.2cm}
\begin{equation}
\prod_{c}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{c}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability, as follows:
%
\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
\begin{align}
  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in the image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}}, \\
  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}.
\end{align}
%
In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and approximate formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively. Note that the choice of mean depth of the object causes some deviation from the exact transmission probability. However, the shift of transmission probability anywhere through the object is still a reasonable approximation as occluded points can only lie outside the object. On the other hand, it yields significant computational savings since ray intersections with an ellipsoid are expensive to evaluate densely.

@@

\begin{figure}
\centering
  \includegraphics[width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}%\\
  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
  \vspace{-0.3cm}
  \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$. The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
  \label{fig:compare:exact:approx:ptrans}
  \vspace{-0.3cm}
\end{figure}

>>>>

%
\begin{wrapfigure}[8]{r}{0.5\textwidth}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \scriptsize
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{wrapfigure}%
%
\vspace{-0.3cm}
\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque and regions more likely to be free space considered more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at 3D location $\ptD$ corresponding to an object $\Obj_i$ centered at $\ObjMu_i$ as
\begin{align}
  \OccF(\ptD) = \Logst(\ptD; \ObjMu_i, \ObjSigma_i),
\end{align}
where $\Logst(\cdot)$ is the logistic function given by
\begin{align}
  \Logst(\ptD; \ObjMu, \ObjSigma) = \frac{1}{1 + e^{-k(1 - \mahaF(\ptD,\ObjMu))}},
\end{align}
with $\mahaF(\ptD, \ObjMu) = (\ptD-\ObjMu)^\top\ObjSigma^{-1}(\ptD-\ObjMu)$ being the Mahalanobis distance. We set $k = 10\ln({49})$ as the value that allows the logistic function $\Logst$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\ObjSigma_i$, depends on the dimensions of the object. Please refer to the supplementary material for the computation of $\ObjSigma_i$ from object dimensions.

\vspace{-0.3cm}
\paragraph{Image formation}
Given the above occupancy representation of the scene, a point on an object is observed in the camera when precisely two conditions are satisfied. First, the backprojected ray from the observed image pixel is transmitted through free space until it reaches the object. Second, the ray encounters an opaque enough object surface and is reflected. More formally, the probability of observation of a point $\ptD_j$ on object $\Obj_i$ is given by
\begin{align}
\Pobs = \PreflR \PtransR
\label{eq:imgform}
\end{align}
The reflection probability ensures the presence of an object to constitute the observation, while the transmission probability allows us to model occlusions. The forms of these two functions are described next.

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\ptD_j$ observed in the image at pixel $\impt_j$. Let $\intm$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\intm^{-1}\impt_j}{\lVert \intm^{-1}\impt_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\impt_j$. Then, the probability of reflection at depth $\dist$ along the ray $\ray$, by an object $\Obj_i$, is determined by the gradient of the object's occupancy function $\OccF^i$ as
\begin{align}
   \Prefl = \frac{1}{Z}(\max \{0, \gOccFi(\ptD_j)^\top \ray \})^2.
\label{eq:evalPrefl}
\end{align}
The gradient $\gOccFi(\ptD_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero. Here, $Z$ denotes the normalization factor. We note that in the extreme case of an object being fully opaque (that is, $\gOccFi(\ptD_j) \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection. Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.

\vspace{-0.3cm}
\paragraph{Transmission probability}
\label{sec:ptransmission}
Since we are modeling occupancy as transparency, we derive inspiration from optics for the modeling of translucent objects. A model for transmission of light across a distance $\alpha$, through a medium of density $\rho$ and opacity $\beta$ is given by the Beer-Lambert law as
\begin{align}
I(\alpha) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\ptD_j$ are encapsulated within the total occupancy function summed over all objects, $\occftot = \sum_i \occf$. Further, the domain of our occupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\dist$ is given by
%
\begin{align}
  \!\!\!\! P^j_{\textit{transmission}}(\dist + d\dist) = P^j_{\textit{transmission}}(\dist) (1-\occftot)^{d\dist}.
\end{align}
%
Thus, for an image point $\impt_j$ to correspond to a 3D point $\ptD_j$ at depth $\dist$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
\PtransR(\dist) = \prod_{c}^{\dist} (1 - \occft{\dist \ray})^{d\dist}.
\label{eq:ptrans-integral}
\end{align}
Here, $\prod_{c}^{\dist}$ represents a \emph{product integral} from $c$ to $\dist$, where $c$ is the position of camera screen, considered here to be equivalent to the focal length of the camera .\footnote{A product integral is a simple integral in the log domain 
\vspace{-0.2cm}
\begin{equation}
\prod_{c}^{\dist} (1 - f_{occ}(\dist \ray))^{d\dist} = e^{\int_{c}^{\dist} \ln{(1 - f_{occ}(\dist \ray))}{d\dist}}. \nonumber
\end{equation}
}

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability, as follows:
%
\begin{align}
  \PtransR(\dist) = \prod_i (1 - \LogstIm (\impt; \tImMu_i, \tImS_i) \LogstD(\dist; \meandepth{i})),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\LogstIm(.)$ is sigmoid in the image domain, with $\tImMu_i$ and $\tImS_i$ representing the elliptical projection of object $\Obj_i$ in the image and $\LogstD(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $\Obj_i$. That is,
%
\begin{align}
\LogstIm(\impt; \tImMu_i, \tImS_i) &= \frac{1}{1 + e^{-k_u(1 - (\impt - \tImMu_i)^\top \tImS_i^{-1} (\impt - \tImMu_i))}}, \\
  \LogstIm(\dist; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\dist - \meandepth{i})}}.
\end{align}
%
In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and approximate formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively. Note that the choice of mean depth of the object causes some deviation from the exact transmission probability. However, the shift of transmission probability anywhere through the object is still a reasonable approximation as occluded points can only lie outside the object. On the other hand, it yields significant computational savings since ray intersections with an ellipsoid are expensive to evaluate densely.

@@

\begin{figure}
\centering
  \includegraphics[width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}%\\
  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
  \vspace{-0.3cm}
  \caption{Comparisons between the approximate and exact formulations of $\Ptrans$. The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
  \label{fig:compare:exact:approx:ptrans}
  \vspace{-0.3cm}
\end{figure}
